---
title: "PsiChiR contest"
author: "Wesley Gardiner"
date: "7/1/2021"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(janitor)
```


Level 1: Create the total superficial judgment summary score (i.e., sum judge_pic, judge_outfit, judge_job, judge_born, judge_live, judge_car, judge_uni, judge_diet, judge_drink, judge_teeth, judge_posts, judge_grammar, judge_sparetime)
```{r}
singleUS <- read_csv("singleUS-singleUS.csv")

summary_scores <- 
  singleUS %>% 
  rowwise() %>%
  mutate(sfj_score = sum(c_across(judge_pic:judge_sparetime))) %>% 
  ungroup()

```
Level 2: Examine the total superficial judgment summary score with a histogram.

```{r}
ggplot(summary_scores, aes(x = sfj_score)) +
  geom_histogram(bins = 50)
```
Level 3: Compute mean/median/mode/standard deviation for the total superficial judgment summary score.

```{r}
summary_scores %>% 
  summarize(mean = mean(sfj_score),
            std_dev = sd(sfj_score),
            med = median(sfj_score),
            most = modeest::mfv(sfj_score)
            )
```


Level 4:Compute means and standard deviation by group & do a t-test



In order to complete each level, you need to complete all levels before (so in order to complete level 4, you also need to do 1, 2, and 3 correctly).







