---
title: "PsiChiR contest"
author: "Wesley Gardiner"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(readr)
library(modeest)
```


## Level 1: 
Create the total superficial judgment summary score (i.e., sum judge_pic, judge_outfit, judge_job, judge_born, judge_live, judge_car, judge_uni, judge_diet, judge_drink, judge_teeth, judge_posts, judge_grammar, judge_sparetime)

```{r}
singleUS <- read_csv("singleUS-singleUS.csv")

summary_scores <-
  singleUS %>%
  rowwise() %>%
  mutate(sfj_score = sum(c_across(judge_pic:judge_sparetime))) %>%
  ungroup()
```

## Level 2: 
Examine the total superficial judgment summary score with a histogram.

```{r}
ggplot(summary_scores, aes(x = sfj_score)) +
  geom_histogram(bins = 30) +
  labs(
    title = "Histogram of Superficial Judgment Summary Scores (SFJ Score)",
    subtitle = "Total yes/no judgment responses by each candidate",
    x = "SFJ Score",
    y = "Number of Responses",
    caption = "Data: OSF PsyChiR Contest"
  ) + 
  scale_x_continuous(breaks=0:13)


```

## Level 3: 
Compute mean/median/mode/standard deviation for the total superficial judgment summary score.

```{r}
summary_scores %>%
  summarize(
    mean = mean(sfj_score),
    std_dev = sd(sfj_score),
    med = median(sfj_score),
    most = modeest::mfv(sfj_score)
  )
```


## Level 4:
Compute means and standard deviation by group & do a t-test


```{r}
summary_scores %>%
  group_by(onenight) %>%
  summarize(
    mean = mean(sfj_score),
    std_dev = sd(sfj_score),
    med = median(sfj_score),
    most = modeest::mfv(sfj_score)
  )

t_test <- summary_scores %>%
  group_by(onenight) %>%
  select(ID, sfj_score, onenight) %>%
  drop_na()

t.test(t_test$sfj_score ~ t_test$onenight)
```


In order to complete each level, you need to complete all levels before (so in order to complete level 4, you also need to do 1, 2, and 3 correctly).
